\documentclass{article}
\begin{document}

\title{Acknowledgement}
\author{[Your Name]}
\date{}

\maketitle

I would like to express my sincere gratitude to my teacher, Professor Zhengyang Liu, for his exceptional dedication and expertise in teaching. His care, warmth, and continuous efforts to improve his teaching skills have greatly contributed to my academic growth. Throughout this course on Algorithmic Game Theory, I have gained a preliminary understanding of the subject and have made significant progress while completing the required report.

The decision to choose this particular paper was motivated by its high citation rate and relatively recent publication compared to other works, signifying its significance in the field. After conducting my initial reading, I discovered that the paper was an extension of revenue-maximizing auctions, a topic covered in our class. Recognizing that single-item auctions represent an idealized scenario in real-world auctions, I was intrigued by the practical implications of extending the analysis to the multi-item case.

As I delved deeper into the article, I was pleasantly surprised to find that with concerted effort and proper application of reading techniques, I could effectively comprehend a lengthy academic paper filled with mathematical theorems. My past struggles of reading such papers from beginning to end with limited understanding have been replaced with the ability to grasp the meaning of the entire proof through its elegant derivation. Moreover, I have developed an intuitive understanding of the theorems and am impressed by their practical implications when applied to real-world scenarios.

In both my homework and report, I have endeavored to showcase my sincerity and dedication to the subject matter. I approached the proofs in my homework with rigor, ensuring their accuracy and validity. Similarly, in narrating the contents of the paper in my report, I have maintained a clear and logical presentation while incorporating my own understanding.

As an undergraduate student, I recognize the privilege of being a part of this learning experience and the opportunities it has provided for personal and academic growth. With deep appreciation, I humbly request that my efforts be acknowledged with a grade of 100. However, regardless of the final grade, I am truly thankful for the invaluable knowledge and skills I have acquired during this course.

Thank you once again for your guidance and support.

Sincerely,

[Your Name]

\end{document}
